%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Software Developer} % Job title
    {Hadish Ertebat e Nasl e No} % Organisation
    {Shiraz, Iran} % Location
    {Aug 2020 - Jul 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the development and maintenance of the accounting program used by the company.}
        \item {Devised a solution to improve the Net Profit calculation in the accounting app and implemented the solution which leads to an increase of 15\% in the profit of the company.}
        \item {Actively participated in code reviews and provided guidance to junior developers on the team.}
        \item {Utilized C\#, SQL, Git, and ASP .Net Core to build efficient, scalable and secure code.
        \\\textbf{Technical Skills:} CI/CD, Microsoft Azure, Back-End Web Development, Microsoft SQL Server, Entity Framework
        \\\textbf{Soft Skills:} Leadership, Problem-solving, Teamwork, Technical Proficiency, Continuous Learning}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
    \cventry
    {System Administrator} % Job title
    {Hadish Ertebat e Nasl e No} % Organisation
    {Shiraz, Iran} % Location
    {May 2017 - Aug 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained the company's computer systems, ensuring their smooth and continuous operation.}
        \item {Quickly troubleshooted and resolved network and computer issues, resulting in a reduction of downtime by 30\%.}
        \item {Configured and managed Microsoft Active Directory, Cisco Routing and Switching, and other network equipment.}
        \item {Implemented a disaster recovery plan that helped the company to recover quickly from unexpected failures.
        \\\textbf{Technical Skills:} Active Directory, Windows Server, Cisco Networking, LAN-WAN, Network Troubleshooting
        \\\textbf{Soft Skills:} Problem-solving, Adaptability, Attention to Detail, Technical Proficiency}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Network Technician (Internship)} % Job title
    {Pars Novin Co.} % Organisation
    {Shiraz, Iran} % Location
    {Feb 2017 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Installed and configured network equipment for clients, including LAN networks and passive equipment.}
        \item {Assisted with the design of network infrastructure, which led to the successful implementation of several projects.}
        \item {Troubleshot and resolved connection problems for clients, resulting in increased customer satisfaction.
        \\\textbf{Technical Skills:} LAN-WAN, Network Design, Network Troubleshooting, IPv4, CCTV Installation
        \\\textbf{Soft Skills:} Teamwork, Communication, Problem solving}
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
    \cventry
    {Store Assistant} % Job title
    {Hadish Computers} % Organisation
    {Shiraz, Iran} % Location
    {May 2015 - Feb 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built strong customer relationships, resulting in a notable 20\% increase in sales and fostering trust and loyalty.}
        \item {Developed in-depth product knowledge to provide accurate information and enable informed purchasing decisions.}
        \item {Adapted sales techniques to meet individual customer needs, enhancing satisfaction and loyalty.
        \\\textbf{Soft Skills:} Relationship Building, Communication, Teamwork, Adaptability}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
