%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
% \begin{minipage}[t]{0.48\linewidth}
  
\begin{cventries}
%---------------------------------------------------------
  \cventry
  {Stock Price Prediction: A Machine Learning Analysis} % Organization/group
  {Data Scientist} % Affiliation/role
  {Exeter, UK} % Location
  {Feb 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Selected stock exchange index data from various countries and employed data science techniques to assess the feasibility of uising Machine Learning models for price trend determination.}
      \item{Explored different Machine Learning techniques, including Regression models with Scikit-learn and time series techniques with Neural Networks using TensorFlow and Keras APIs for Python.}
      \item{Ensured data robustness and correctness through a data cleaning and preprocessing pipeline using Pandas and NumPy libraries for Python.}
      \item{Effectively communicated results and findings using data visualization techniques with the Matplotlib Python library.}
    \end{cvitems}
  }%
%---------------------------------------------------------
  \cventry
  {Tweeter : An Analysis of tweets statistics}
  {Data Scientist}
  {Exeter, UK}
  {Nov 2022}
  {
    \begin{cvitems}
      \item {Tasked with analyzing one month of tweets (100GB data) posted from Europe, I used the Twitter API, streamed the data, and processed it with NumPy and Pandas.}
      \item{Explored various tweet statistics, including user tweet counts, regional activity on weekdays vs. weekends, and user distribution through geospatial attributes.}
      \item{Conducted advanced analysis by cross-referencing word maps with country-specific hot topics to infer correlations.}
      \item{Communicated the findings using Matplotlib for data visualization and Latex for report writing.}
    \end{cvitems}
  }%
%---------------------------------------------------------
%   \end{cventries}
% \end{minipage}
% \hspace{0.04\linewidth}
% \begin{minipage}[t]{0.48\linewidth}
% \begin{cventries}
  %---------------------------------------------------------
  \cventry
  {Foodic Startup Project} % Organization/group
  {Software Developer} % Affiliation/role
    {Shiraz, Iran} % Location
    {Jun 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item{Pitched and singd a startup opportunity with DIMOND accelerator during a startup weekend event.}
        \item{Efficiently developed a demo software stack for the project within a three-day timeframe.}
        \item{Developed an Android application in Java and designed a Telegram bot and a website using C\# with .Net and SQL, showcasing technology utilization in an agile environment.}
      \end{cvitems}
    }%
%---------------------------------------------------------
  % \cventry
  %   {Developer} % Affiliation/role
  %   {Drone Auto-pilot Board} % Organization/group
  %   {Shiraz, Iran} % Location
  %   {Mar 2016 - Oct 2016} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Designed and implemented the circuit board.}
  %       \item {Implemented the PID controller with C++.}
  %       \item {Gained experience in embeded programming.}
  %       \item {Developed an understanding of circuit boards.}
  %     \end{cvitems}
  %   }%
%---------------------------------------------------------
  % \cventry
  %   {C++ Programmer} % Affiliation/role
  %   {East-Asia ACM Coding Contest} % Organization/group
  %   {Tehran, Iran} % Location
  %   {2014, 2016, 2017} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Developed strategies for solving given problems and implemented the agreed upon strategies with teammates.}
  %     \end{cvitems}
  %   }%
%---------------------------------------------------------
\end{cventries}
% \end{minipage}
% \vspace{3mm}\\